---
title: "01_Exploratory Data Analysis"
author: "Anjali Gupta"
date: "23 April 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
```

```{r set-options, echo=FALSE, cache=FALSE}
options(width = 80)
```

## Read Data

```{r, echo = TRUE}
data_eda <- mpg
```

## Summary using package: skimr

```{r, echo = TRUE}
library(skimr)
fix_windows_histograms()
skim(data_eda)
```

## Summary using package: summarytools

Function: dfSummary

```{r, echo = TRUE}
library(summarytools)
dfSummary(data_eda, style = "grid")#graph.magnif = 0.75,
```

## Summary using package: Hmisc

```{r, echo = TRUE}
library(Hmisc)

describe(data_eda)
```


## NOT REQUIRED

## Summary using package: pastecs

Does not summarise character variables.

```{r, echo = TRUE}
library(pastecs)

stat.desc(data_eda)
```

## Summary using package: psych

Does not summarise character variables.

```{r, echo = TRUE}
library(psych)

describe(data_eda)
```

## Summary using package: summarytools

Function: descr

Does not summarise character variables.

```{r, echo = TRUE}


descr(data_eda)
```