---
title: "02_Summary"
author: "Anjali Gupta"
date: "23 April 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
library(dplyr)
library(ggplot2)
library(skimr)
library(summarytools)
library(Hmisc) #Not used in the output file at the moment
library(xlsx)
library(stringi)
```

```{r set-options, echo=FALSE, cache=FALSE}
options(width = 80)
```

*PURPOSE*

This code creates a detailed **Exploratory Analysis** report for any dataset.

*OUTPUT*

The output is saved in an excel workbook, where the first worksheet summarises all the fields present in the dataset. The subsequent worksheets summarise individual variables in the dataset.

*REQUIREMENT*

Specify the input file name in the below R chunk.

## Read Data

```{r, echo = FALSE}
data_eda <- mpg
#data_eda <- read.csv("xxx.csv", header=TRUE)
```

## Summary using package: skimr

```{r, echo = FALSE}
fix_windows_histograms()
skim_with(numeric = list(distinct = n_distinct), integer = list(distinct = n_distinct))
summary_skim <- skim_to_wide(data_eda)
```

## Summary using package: summarytools

Function: dfSummary

```{r, echo = FALSE}
summary_dfsummary <- dfSummary(data_eda, style =  "grid")
```

## Summary using package: Hmisc

This output is not used in the output file at the moment.

```{r, echo = TRUE}
(summary_describe <- describe(data_eda))
```

## Write output to excel workbook

```{r, echo = FALSE}
write.xlsx(summary_skim, file = "EDA.xlsx", sheetName = "Summary", append = FALSE)
```

```{r, echo = FALSE}
for(i in 1:nrow(summary_dfsummary)){
  sheetname <- strsplit(summary_dfsummary$Variable[i], "[\\\n]")[[1]][1]
  
  stats_values <- strsplit(summary_dfsummary[i,3], "[\n]")[[1]]
  freqs_percofvalid <- strsplit(summary_dfsummary[i,4], "[\n]")[[1]]
  
  if(length(stats_values) == length(freqs_percofvalid)){
    subsummary_dfsummary <- data.frame(stats_values, freqs_percofvalid)  
  }else{
    diff <- length(stats_values) - length(freqs_percofvalid)
    subsummary_dfsummary <- data.frame(stats_values, "freqs_percofvalid" = c(freqs_percofvalid, rep("", diff)))
  }
  
  write.xlsx(subsummary_dfsummary, file = "EDA.xlsx", sheetName = sheetname, append = TRUE, row.names = FALSE) 
}
```